\section{Conclusion}
\label{Conclusion}
%
The research conducted in this study revealed 10 main categories relating to HRI. Attributes were found for each of these 10 categories which describe the user experience of interacting with a social robot at Aalborg Airport. The observations and the 30 subjects' statements were interpreted and coded using an affinity diagram. 567 affinity notes were sorted by a bottom-up procedure into 10 categories which revolved around appearance, trust, behaviour, approach, problems with the touch screen, avoidance of interaction, personal interest, positivity towards the robot, usefulness, and tech-experience.

New attributes within the 10 categories were discovered compared to previous mentioned studies: Elegance, cuteness, coolness, startling, excitement, welcoming, obstructive, whether the robot help is seen as personal, and whether the encounter with the robot was surprising. Besides the newly found attributes some attributes were found to match previously found attributes. These attributes regards distance, anthropomorphism, height, speed, movement, trust, and usefulness.

23 attributes were elicited and scales were developed from these. After the second test, 10 instances of correlations were found for both height and distance and 9 for direction based on PCA with different groupings. 12 instances of correlation were found when comparing attributes that correlates when conducting PCA.

Based on the results in this study, it is suggested that the scale questions: \textit{I relied on the robot to lead me to the location I chose} and \textit{I feel safe around the robot} are combined to one attribute named: Trust. Also funny and cool are described by exciting and cute and thus seem redundant. Finally, the scale question: \textit{I like to be served by the robot} is also described by intrusive and exciting, thus also seem redundant.

The different types of scales used in this study could explain the difference in variance between the scales. The closed endpoints might affect how much the results accumulate at the ends. The label \textit{fine}, the use of midpoints, and scale questions such as \textit{I think the robot stopped...} should be reconsidered to improve the user's understanding of the scale and minimize misunderstandings. 

%\subsection{Future work}
%{\color{red} Dette afsnittet slettes helt, da det nu er udført}
%\sout{During the next month, the evaluation of the scales will take place at AAL. This involves creating the scales from the results of the affinity diagram, bringing the robot to the airport, letting travellers interact with it, measuring their experience on the developed scales, and analysing the results.}